Creating an Arrow IPC file from the NYC 311 data

### 2023-06-17 nyc311clean.qmd
Add an example reading Arrow with polars

or Python (not that this format is called `feather` in the `pyarrow` package)

@@

>>>>

or Python (note that this format is called `feather` in the `pyarrow` package)

@@

>>> import polars as pl
>>> df = pl.read_ipc("./data/311_half_March_2023.arrow", use_pyarrow=True)
>>> df
shape: (125_826, 46)
┌────────────┬────────────┬──────────────┬────────┬───┬────────────┬──────────────┬──────────────┬──────────────┐
│ Unique_Key ┆ Created_Da ┆ Closed_Date  ┆ Agency ┆ … ┆ Community_ ┆ Borough_Boun ┆ City_Council ┆ Police_Preci │
│ ---        ┆ te         ┆ ---          ┆ ---    ┆   ┆ Districts  ┆ daries       ┆ _Districts   ┆ ncts         │
│ i32        ┆ ---        ┆ datetime[ms] ┆ cat    ┆   ┆ ---        ┆ ---          ┆ ---          ┆ ---          │
│            ┆ datetime[m ┆              ┆        ┆   ┆ i8         ┆ i8           ┆ i8           ┆ i8           │
│            ┆ s]         ┆              ┆        ┆   ┆            ┆              ┆              ┆              │
╞════════════╪════════════╪══════════════╪════════╪═══╪════════════╪══════════════╪══════════════╪══════════════╡
│ 57000688   ┆ 2023-03-09 ┆ 2023-03-13   ┆ DOE    ┆ … ┆ 2          ┆ 2            ┆ 27           ┆ 39           │
│            ┆ 15:05:25   ┆ 08:21:11     ┆        ┆   ┆            ┆              ┆              ┆              │
│ 56993837   ┆ 2023-03-08 ┆ 2023-05-03   ┆ TLC    ┆ … ┆ 23         ┆ 4            ┆ 51           ┆ 11           │
│            ┆ 21:27:34   ┆ 07:17:20     ┆        ┆   ┆            ┆              ┆              ┆              │
│ 57049479   ┆ 2023-03-15 ┆ 2023-03-21   ┆ HPD    ┆ … ┆ 8          ┆ 5            ┆ 43           ┆ 24           │
│            ┆ 19:26:41   ┆ 21:16:53     ┆        ┆   ┆            ┆              ┆              ┆              │
│ 57056381   ┆ 2023-03-16 ┆ 2023-03-17   ┆ NYPD   ┆ … ┆ 49         ┆ 5            ┆ 35           ┆ 23           │
│            ┆ 23:58:53   ┆ 02:44:31     ┆        ┆   ┆            ┆              ┆              ┆              │
│ …          ┆ …          ┆ …            ┆ …      ┆ … ┆ …          ┆ …            ┆ …            ┆ …            │
│ 56954525   ┆ 2023-03-04 ┆ 2023-03-08   ┆ DEP    ┆ … ┆ 12         ┆ 4            ┆ 10           ┆ 6            │
│            ┆ 16:23:00   ┆ 10:50:00     ┆        ┆   ┆            ┆              ┆              ┆              │
│ 57132547   ┆ 2023-03-24 ┆ 2023-03-24   ┆ NYPD   ┆ … ┆ 30         ┆ 1            ┆ 14           ┆ 76           │
│            ┆ 21:57:44   ┆ 23:18:11     ┆        ┆   ┆            ┆              ┆              ┆              │
│ 57102740   ┆ 2023-03-21 ┆ 2023-03-21   ┆ NYPD   ┆ … ┆ 70         ┆ 4            ┆ 32           ┆ 4            │
│            ┆ 05:10:12   ┆ 05:16:30     ┆        ┆   ┆            ┆              ┆              ┆              │
│ 56950149   ┆ 2023-03-04 ┆ 2023-03-04   ┆ DOT    ┆ … ┆ 41         ┆ 3            ┆ 16           ┆ 61           │
│            ┆ 00:27:00   ┆ 10:15:00     ┆        ┆   ┆            ┆              ┆              ┆              │
└────────────┴────────────┴──────────────┴────────┴───┴────────────┴──────────────┴──────────────┴──────────────┘
